|

### 2020-09-22 paper/paper.Rmd
small changes to algorithm sections

Figure \ref{fig:cdf} compares these two quantities (equations \ref{eq:cdf} and \ref{eq:vp}), for $p=3, 10, 100$. At left is $v_{2} (r; p, R)$ and on the right is $v_{p} (r; p, R)$. The function shapes change in opposite directions as $p$ increases: $v_{2} (r; p, R)$ peaks earlier and $v_{p} (r; p, R)$ gets flatter. This is the paradox of the curse of dimensionality in that projected volume at the center increases with $p$.

@@

The full radial transformation is therefore given by 
\begin{equation}
r'_y = v_2^{-1} (v_2(r_y; p, R); 2, R) =  R \sqrt{v_2(r_y; p, R)} = R \sqrt{1-\left(1-\left(\frac{r_y}{R}\right)^2\right)^{p/2}}.
\label{eq:resc}
\end{equation}

The relation between $r'_y$ and $r_y$ depends on the number of dimensions $p$, and is illustrated for selected values in Figure \ref{fig:radii}. We see that the transformation is approximately linear near the center. As $p$ increases it becomes non-linear faster, and e.g. for $p=10$ the points with radius $r_y>0.5$ will already be highly distorted and pushed out towards the last eighth in $r'_y$. Figure \ref{fig:circles} demonstrates this for different values of $p$ by showing equidistant circles for which the radius has been transformed according to Eq. \ref{eq:resc}.

@@

The transformation in Eq. \ref{eq:resc} is fixed for a given input dataset, by evaluating the number of dimensions $p$ and the maximum distance from the center $R$. However, in realistic applications we may wish to trim the projected data or tune the transformation. In practice, a combination of both adjustments can be used to further zoom in on the center of the distribution, or alternatively, to soften the transformation.

@@

We allow tuning $p_{\mathrm{eff}} = \gamma p$ by selecting the scaling parameter $\gamma$. By default, $\gamma=1$ and $p_{\mathrm{eff}}=p$. When $\gamma<1$ the rescaling will be softer, and $\gamma>1$ results in more aggressive rescaling than suggested by $p$ alone. Note that when $p_{\mathrm{eff}} < 2$ we actually invert the behavior and shift the focus away from the center, in general this is not wanted.

>>>>

Figure \ref{fig:cdf} compares these two quantities (Eq. \ref{eq:cdf} and \ref{eq:vp}), for $p=3, 10, 100$. At left is $v_{2} (r; p, R)$ and on the right is $v_{p} (r; p, R)$. The function shapes change in opposite directions as $p$ increases: $v_{2} (r; p, R)$ peaks earlier and $v_{p} (r; p, R)$ gets flatter. This is the paradox of the curse of dimensionality in that projected volume at the center increases with $p$.

@@

The full radial transformation is therefore given by 
\begin{equation}
r'_y = v_2^{-1} (v_2(r_y; p, R); 2, R) =  R \sqrt{v_2(r_y; p, R)} = R \sqrt{1-\left(1-\left(\frac{r_y}{R}\right)^2\right)^{p/2}}
\label{eq:resc}
\end{equation}

The relation between $r'_y$ and $r_y$ depends on the number of dimensions $p$, and is illustrated for selected values in Figure \ref{fig:radii}. We see that the transformation is approximately linear near the center. As $p$ increases it becomes non-linear faster, and for $p=10$, for example, the points with radius $r_y>0.5$ will already be highly distorted and pushed out towards the last eighth in $r'_y$. Figure \ref{fig:circles} demonstrates this for different values of $p$ by showing equidistant circles for which the radius has been transformed according to Eq. \ref{eq:resc}.

@@

The transformation in Eq. \ref{eq:resc} is fixed for a given input dataset, by evaluating the number of dimensions $p$ and the maximum distance from the center $R$. However, in practice we may wish to trim the projected data or tune the transformation. A combination of both adjustments can be used to further zoom in on the center of the distribution, or alternatively, to soften the transformation.

@@

We allow tuning $p_{\mathrm{eff}} = \gamma p$ by selecting the scaling parameter $\gamma$. By default, $\gamma=1$ and $p_{\mathrm{eff}}=p$. When $\gamma<1$ the rescaling will be softer, and $\gamma>1$ results in more aggressive rescaling than suggested by $p$ alone. Note that when $p_{\mathrm{eff}} < 2$ we actually invert the behavior and shift the focus away from the center, in general this is not recommended.
